---
title: "D2SC ICMA Notebook"
author: "Jennifer Curi"
date: "`r Sys.Date()`"
output:
  word_document:
    
    toc: yes
  pdf_document:
    toc: yes
  html_document:
    df_print: paged
    toc: yes
    toc_depth: 2
    toc_float: 
      collapsed: false
---

```{r}
knitr::opts_chunk$set(echo=FALSE)
```


```{r load-libraries, echo=FALSE, message=FALSE}
library(tidyverse)
```

# ICMA September 9 2024

```{r}

# this is a comment
plot(cars)
```

# ICMA September 11 2024
```{r}

2+2

```

```{r}

x <- 2+2

```

```{r}

x 

```
```{r}

?(mean)

```


```{r}

help(mean)

```

```{r}

mean(c(2,3,4))

```

```{r}

myVector <- (c(2,3,4))

```

```{r eval=FALSE}
mean(my_vector)
```
doesnt initialize until after it is veab used

```{r}

my_vector <- (c(2,3,4))

```

```{r}

myVector

```

```{r}

?sd
help(sd)

```

```{r}

sd(1:2) ^2

```



# ICMA September 16 2024

```{r}
library(tidyverse)
```

```{r eval=FALSE}

stats::filter()

```

```{r eval=FALSE}
head(3, billboard)
#does not work
```

```{r}

#pipe -> takes outcome and passes it to the next function 


```

```{r}
#create a vector of num

my_numbers <- c(1, 2, 3, 4, 5, 6, 7, 8, 9, 10)
```

```{r}

#without pipe
mean(my_numbers)


```


```{r}
my_numbers %>%
  mean()
```



```{r}
getwd()

#working directory
```


```{r}
help(mtcars)
#description of dataset
```


```{r}
mtcars
```






```{r}
write_csv(mtcars, #object name
          "mtcars_fromR.csv" #file name to save
          )
#writing data set
#no columns
```

```{r}
mtcars %>%
  rownames_to_column() %>%
  write_csv("mtcars_fromR_rownames.csv")

#adds columns
```


```{r}
mtcars_read <- read_csv("data/mtcars_fromR_rownames.csv")

#read csv
#assign as a variable

```

# ICMA September 18 2024

```{r}
? ChickWeight
```

```{r}
glimpse(ChickWeight)
```

```{r}
ChickWeight %>%
  select(Chick,weight) %>% #keep Chick and Weight
  head(n=3) #view just three rows
```

```{r}
ChickWeight %>%
  select(age_days = Time, weight_gm = weight) %>% #renaming while keeping
  head(n=3)
```

```{r}
ChickWeight %>%
  select(-weight) %>% #drop a column
  head(n=3)
```

```{r}
#will not change original object
ChickWeight %>%
  select(age_days = Time, weight_gm = weight) %>%
  head() #to restrict preview
```

```{r}
#will replace original object
ChickWeight <- ChickWeight %>%
  select(age_days = Time, weight_gm = weight)
```

```{r eval=FALSE}
#will save the modified object in a new object
ChickWeightModified <- ChickWeight %>%
  select(age_days = Time, weight_gm = weight)
```

```{r eval=FALSE}
chick_clean <- ChickWeight %>% #assigning to a new object chick_clean
  select(chick_id = Chick,
         diet = Diet,
         age_days = Time,
         weight_gm = weight) #renaming %re-ordering while keeping
```

```{r eval=FALSE}
chick_clean %>%
  filter(age_days <10) %>%
  head(n = 6)
```


```{r eval=FALSE}
chick_clean %>%
  filter(chick_id == 1) %>%
  head(n = 6)
```











```{r eval=FALSE}
chick_clean %>%
  arrange(age_days) %>%
  head() # just for preview
```


```{r eval=FALSE}
chick_clean %>%
  arrange(chick_id) %>%
  head() # just for preview
```


```{r eval=FALSE} 
chick_clean %>%
  mutate(new_column = "value") %>%
  head(n = 3)
```

```{r eval=FALSE}
chick_clean %>%
  mutate(weight_per_day = weight_gm/age_days) %>%
  head(n = 3)
```


```{r eval=FALSE}
chick_clean %>%
  mutate(session = case_when(age_days == 0 ~ "birth",
                             age_days == 20 ~ "last1",
                             age_days == 21 ~ "last2",
                             TRUE           ~ as.character(age_days)))
```


```{r eval=FALSE}
chick_clean %>%
  summarise(mean_weight = mean(weight_gm),
            N = n())
```


```{r eval=FALSE}
chick_clean %>%
  group_by(age_days) %>% ## grouping variable
  summarise(mean_weight = mean(weight_gm),
            N = n()) ## creates a column that summarizes the data based on the grouping variable

```

```{r eval = FALSE}
grouped <- chick_clean %>%
  group_by(age_days)
```
```{r eval=FALSE}
chick_clean %>%
  glimpse()
```

```{r eval =FALSE}
grouped %>%
  glimpse()
```

```{r eval =FALSE}
chick_clean %>%
  summarise(mean_weight = mean(weight_gm))

```

```{r eval =FALSE}
grouped %>%
  summarise(mean_weight = mean(weight_gm))
```

```{r eval=FALSE}
grouped %>%
  ungroup() %>%
  summarise(mean_weight = mean(weight_gm))
```

```{r eval=FALSE}
ChickWeight %>%
  distinct(Chick) %>%
  count() %>%
  head(n=3)
```


# ICMA September 23 2024

```{r}
head(billboard)
```

```{r}
billboard %>%
  pivot_longer(wk1:wk76)

```

```{r}
billboard_long <- billboard %>%
  pivot_longer(cols=starts_with("wk"),
               names_to = "week",
               values_to = "position")

```


```{r}
head(billboard_long)
```
```{r}
dim(billboard)
```

```{r}
billboard_long %>%
  pivot_wider(names_from = week,
              values_from = position)
```

```{r}
?pivot_longer
```


```{r}
billboard %>%
  pivot_longer(cols=starts_with("wk"),
               names_to = "week",
               values_to = "position",
               names_prefix = "wk",
               values_drop_na = TRUE)
```


```{r}
billboard %>%
  separate(col = date.entered,
          into = c("year", "month", "day"))
             
```





# ICMA September 25 2024

```{r}
head(ChickWeight)
```


```{r}
ChickWeight %>%
  ggplot() #empty ggplot function
```


```{r eval=FALSE}
ChickWeight %>%
  ggplot(aes(y = weight,
             x = Time,
             color = Diet)) +
  geom_point(alpha = 0.5) + 
  geom_smooth(se = FALSE) + 
  theme_minimal() + 
  
  
  labs(y = "weight in grams",
       x = "days since birth",
       title = "Weight Over Time Across Diets")
```
```{r}
ggsave("chick_weightovertime.png",
     width = 9,
       height = 8)
```

```{r eval=FALSE}
ChickWeight %>%
  ggplot(aes(y = weight,
             x = Time,
             color = Diet)) +
  geom_boxplot(alpha = 0.5) + #make these a little transparent
 # geom_smooth(se = FALSE) + #removing the error bands
  theme_minimal() + # using a pre-made theme to change the appearance, which we can further modify!
  
  facet_grid(~Diet) + # faceting by diet group
  
  labs(y = "weight in grams",
       x = "days since birth",
       title = "Weight Over Time Across Diets")
```












# ICMA October 7 2024
```{r}
as.numeric("eighteen")
```

```{r}
((1 + 2) < -1000) | (TRUE & NA)
```

```{r}
((1 + 2) < -1000) | (TRUE | NA)
```

```{r}
(2 + 3 + 9 - 4 == 2 + 6 + as.integer("2.9")) & TRUE | NA
```


```{r}
(TRUE && TRUE | FALSE) & (TRUE && FALSE && NA)
```



# ICMA October 9 2024

```{r}
my_number <- 12
```

```{r}
age_data <- tribble(
                    ~ id, ~ age,
                    1, 8,
                    2, 10,
                    3, 8,
                    5, 9
            )

gender_data <- tribble(
                    ~ id, ~ gender,
                    1, "f",
                    2, "m",
                    3, "nb",
                    4, "m",
                    6, "f"
            )


gender_data_BADID <- tribble(
                    ~ id_x, ~ gender,
                    1, "f",
                    2, "m",
                    3, "nb",
                    4, "m",
                    6, "f"
            )
```


```{r}
age_data
```

```{r}
gender_data

```


```{r}
full_join(age_data, gender_data)

```

```{r}
full_join(gender_data_BADID, age_data, by = join_by(id_x == id))

```

```{r}
full_join(age_data, gender_data_BADID, by = join_by(id == id_x))

```

```{r}
right_join(age_data, gender_data)

```


```{r}
left_join(age_data, gender_data)

```

```{r}
inner_join(age_data, gender_data)

```


```{r eval=FALSE}
bind_cols(gender_data, age_data)

```

```{r eval=FALSE}
bind_cols(age_data_4, gender_data_4)

```


```{r eval=FALSE}
bind_rows(age_data_4, gender_data_4)

```















# ICMA October 16 2024

```{r}
mean(c(1, 2, 3))
```


```{r}
(1 + 2 + 3)/3
```

```{r}
vec <- c(1, 2, 3)
```

```{r}
(vec[1] + vec[2] + vec[3])/length(vec)
```

```{r}
fave_number <- tribble(~name, ~number,
                       "MC", 8,
                       "AP", 9,
                       "NG", 12,
                       "VE", 6,
                       "AL", 17,
                       "AR", 3,
                       "MC", 7,
                       "RK", 8,
                       "AC", 4,
                       "SC", 21,
                       "KK", 16,
                       "RK", 28,
                       "VK", 17,
                       "MH", 12)
```

```{r}
for (i in fave_number) {
  print(i)
}
```

```{r}
class(fave_number)
```

```{r}
for (i in fave_number["number"]) {
  print(i)
}
```


```{r}
for (i in fave_number$number) {
  print(i)
}
```
```{r}
length(fave_number$number)

```

```{r}
length(fave_number["number"])

```

Why is the output different? How are fave_number[“number”] and fave_number$number different?
```{r}
typeof(fave_number["number"])

```

```{r}
typeof(fave_number$number)
```

```{r}
for (i in fave_number[["number"]]) {
  print(i)
}
```

```{r}
str_c("takes vectors", "and puts them", "together", sep = " ")

```

```{r}
for (i in seq_along(fave_number$name)) {
  
  print(str_c(fave_number$name[i], "'s favorite number is ", fave_number$number[i]))
  
}
```
```{r}
mtcars

```












# ICMA October 30 2024

write a sentence that has **bold** and *italics*

Part 2: creatw a variable then write a sentance that uses that variable, bold and italics. 

```{r}
name <- "Jen"
```

My name is `r name` and I *like* **Chick-fil-a**

```{r}
ChickWeight <- ChickWeight
```

```{r chick-plot, fig.cap= "Weight across age days"}
ChickWeight %>%
  ggplot(aes(y= age_days, x= weight_gm)) +
  geom_line()
```


# ICMA December 2, 2024

```{r}
install.packages("forcats")
```

```{r}
months <- c("April", "Dec", "Jan","Feb","March")
```

```{r}
sort(months)
```

```{r}
months_base <- factor(months,
                 levels = c("Jan", "Feb", "March", "April", "Dec"))
```

```{r}
months_base
```

```{r}
library(forcats)
```

```{r}
months_forcats <- fct(months,
                      levels = c("Jan", "Feb", "March", "April","May","June","July", "Dec"))
```


```{r}
months_forcats
```

```{r}
factor(months,
      levels = c("Jan", "Feb", "March", "April","May","June","July", "Dec")     
)

```








