---
title: A Better Reproducible Poster Title
author:
  - name: Brent Thorne
    affil: 1
    twitter: brentthorne18
    email: brentthorne18@gmail.com
    orcid: 0000-0002-1099-3857
    main: true
affiliation:
  - num: 1
    address: Department of Earth Sceicnes, Brock University
output: 
  posterdown::posterdown_betterland:
    self_contained: false
    pandoc_args: --mathjax
    highlight: haddock
    number_sections: false
link-citations: true
bibliography: packages.bib
---

```{r, include=FALSE}
knitr::opts_chunk$set(results = 'asis',
                      echo = FALSE,
                      warning = FALSE,
                      tidy = FALSE,
                      message = FALSE,
                      fig.align = 'center',
                      out.width = "100%")
options(knitr.table.format = "html") 
```

```{r myplot, include=FALSE}
library(tidyverse)
library(ggdist)
library(ggplot2)
```

```{r}
setwd("/Users/jencuri/Documents/GitHub/Data2SciComm/Project_Data")
```

```{r}

indexes_df <- readxl::read_excel('/Users/jencuri/Documents/GitHub/Data2SciComm/Project_Data/indexes.xlsx', sheet = 'exp1')
indexes_df2 <- readxl::read_excel('/Users/jencuri/Documents/GitHub/Data2SciComm/Project_Data/indexes.xlsx', sheet = 'exp2')
db_df <- read_csv('/Users/jencuri/Documents/GitHub/Data2SciComm/Project_Data/DB.csv')

```

```{r clean_data, echo=TRUE}
# Remove rows with NA values for analysis
db_df <- na.omit(db_df)
df_combined <- na.omit(bind_rows(
  indexes_df %>% mutate(Experiment = "Exp 1"),
  indexes_df2 %>% mutate(Experiment = "Exp 2")
))
```

```{r standardize_data, echo=TRUE}
# Standardize the intensity index for both experiments
if("intensity_index" %in% colnames(df_combined)) {
  df_combined <- df_combined %>%
    group_by(Experiment) %>%
    mutate(z_intensity_index = (intensity_index - mean(intensity_index)) / sd(intensity_index)) %>%
    ungroup()
}
```

```{r data_summary, echo=TRUE}
# Summary of the data to check for issues
print("Summary of Combined Dataset:")
print(summary(df_combined))
```

```{r summary_stats, echo=TRUE}
# Calculate and print mean and standard deviation for each gender within each experiment
print("Mean and Standard Deviation by Gender and Experiment:")
summary_stats <- df_combined %>%
  group_by(Experiment, Sex) %>%
  summarise(mean_intensity = mean(z_intensity_index, na.rm = TRUE),
            sd_intensity = sd(z_intensity_index, na.rm = TRUE))
print(summary_stats)
```

```{r plot1_reaction_times_combined, echo=TRUE}
plot1_reaction_times_avg <- db_df %>%
  ggplot(aes(x = CS, y = rt, color = res)) +
  stat_summary(fun = mean, geom = "point", size = 4) +
  stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, color = "black") +
  labs(title = "Reaction Times by Cue Type (Mean with Error Bars, by Response Type)",
       x = "Cue Type", y = "Reaction Time (ms)", color = "Response Type") +
  theme_minimal()

# Display the Reaction Times Average plot
print(plot1_reaction_times_avg)
```





```{r plot3_interaction_plot, echo=TRUE}
# Plot 3: Interaction Plot for Standardized Intensity Bias by Gender and Experiment (Using ggdist for Distribution)
if("z_intensity_index" %in% colnames(df_combined)) {
  interaction_plot <- df_combined %>%
    ggplot(aes(x = Experiment, y = z_intensity_index, color = Sex, fill = Sex)) +
    stat_summary(fun = mean, geom = "line", size = 1.5, aes(group = Sex), linetype = "solid") +
    stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2, aes(group = Sex), color = "black") +
    stat_summary(fun = mean, geom = "point", size = 4) +
    stat_slab(aes(fill = Sex), alpha = 0.3, color = NA) +
    geom_jitter(aes(y = z_intensity_index), width = 0.1, alpha = 0.4, size = 1, color = "grey50") +
    labs(title = "Interaction Plot: Standardized Intensity Bias by Gender and Experiment (Using ggdist)",
         x = "Experiment", y = "Standardized Intensity Bias Index (Z-score)", color = "Gender", fill = "Gender") +
    theme_minimal()

  # Display the Interaction Plot
  print(interaction_plot)
}
```

```{r plot4_direction_bias, echo=TRUE}
# Plot 4: Direction Bias by Gender (Side-by-Side Boxplots for Each Experiment with ggdist)
direction_bias_boxplot <- df_combined %>%
  ggplot(aes(x = Sex, y = direction_index, fill = Sex)) +
  stat_halfeye(adjust = 0.7, width = 0.6, justification = -0.2) +
  geom_boxplot(width = 0.3, position = position_dodge(width = 0.6)) +
  facet_wrap(~ Experiment) +
  stat_summary(fun = mean, geom = "point", size = 4, color = "black", position = position_dodge(width = 0.6)) +
  geom_jitter(aes(y = direction_index), width = 0.1, alpha = 0.4, size = 1) +
  labs(title = "Direction Bias by Gender and Experiment (Using ggdist)",
       x = "Gender", y = "Direction Bias Index") +
  theme_minimal()

# Display the Direction Bias Boxplot
print(direction_bias_boxplot)
```



# Introduction

Understanding how humans can respond to different motivational cues can be pretty complex. This project explores the affect of both rewarding and punishing cues on human behavior, focusing on the differences in responses between men and women. Participants were presented with a series of cues and asked to respond under different conditions. The purpose of my project is to understand how these cues impact reaction times and examine any potential gender-based differences in intensity and direction bias. In this project, I will analyzed how the participants' responses might differ across different experimental setups. I will look close at the recorded responses between reaction time, intensity bias, direction bias.


```{r, include=FALSE}
knitr::write_bib(c('posterdown', 'rmarkdown','pagedown'), 'packages.bib')
```

## Objectives

1. Pick a template layout.
2. Write/ create your poster content distraction free.
3. Let posterdown do its thing!

# Methods

I will show here how to include poster elements that may be useful, such as an equation using mathjax:

$$
E = mc^2
$$

To reference a citation you can add your `.bib` file to the working directory and name it in the YAML metadata or generate an automated one as done here, then you only need to reference the label value in the `.bib` file. For example this package is built on top of the wonderful {pagedown} package and I will cite it at the end of this sentance using this in the rmd `[@R-pagedown]` [@R-pagedown].

To get a better understanding of how to include features like these please refer to the {posterdown} [wiki](https://github.com/posterdown/wiki).

**_Now on to the results!_**

<br>

# Results

Here you may have some figures to show off, bellow I have made a scatterplot with the infamous Iris dataset and I can even reference to the figure automatically like this, `Figure \@ref(fig:irisfigure)`, Figure \@ref(fig:irisfigure).

```{r, irisfigure, fig.cap='Here is a caption for the figure. This can be added by using the "fig.cap" option in the r code chunk options, see this [link](https://yihui.name/knitr/options/#plots) from the legend himself, [Yihui Xie](https://twitter.com/xieyihui).', out.width="80%"}
par(mar=c(2,2,0,1))
plot(x = iris$Sepal.Length, y = iris$Sepal.Width,
     col = iris$Species, pch = 19, xlab = "Sepal Length",
     ylab = "Sepal Width")
```

Maybe you want to show off some of that fancy code you spent so much time on to make that figure, well you can do that too! Just use the `echo=TRUE` option in the r code chunk options, Figure \@ref(fig:myprettycode)!

```{r myprettycode, echo=FALSE,collapse=TRUE, fig.cap='Boxplots, so hot right now!', fig.height=3.5, out.width="80%"}
#trim whitespace
par(mar=c(2,2,0,0))
#plot boxplots
boxplot(iris$Sepal.Width~iris$Species,
        col = "#008080", 
        border = "#0b4545",
        ylab = "Sepal Width (cm)",
        xlab = "Species")
```

How about a neat table of data? See, Table \@ref(tab:iristable):

```{r, iristable}
knitr::kable(
  iris[1:8,1:5], format = "html",
  caption = "A table made with the **knitr::kable** function.",
  align = "c", col.names = c("Sepal <br> Length",
                             "Sepal <br> Width",
                             "Petal <br> Length",
                             "Petal <br> Width",
                             "Species"),
  escape = FALSE)
```

# References
