---
title: "D2SC: Weekly Assignments"
author: "Jennifer Curi"
date: "`r Sys.Date()`"
output: html_notebook
---

# Initial Loading

```{r}
# loads tidyverse library
library(tidyverse)
```

# Week 1

I used Google to figure out how to load the tidyverse library. Specifically "How to add a 
code chunk that loads the tidy verse library".From there, I made sure to to use different credible websites to ensure that I find the correct code. The first website I opened was 
Stack Overflow (https://stackoverflow.com/questions/58289197/how-to-write-an-r-chunk-to-load-the-tidyverse).

However, I noticed that the comments were asking the user to clarify his question (i.e R Setup, or R Notebook, R Markdown). From this I employed another search clarifying that I am 
using R Notebook. From there I looked at another Stack Overflow forum (https://stackoverflow.com/questions/58568048/tidy-verse-issue) and I also looked at the 
 Tidyverse documentation (https://tidyverse.tidyverse.org/) on how to use the library. 
 
 To check that it was working, I ran the code and compared my Console output to the Tidyverse documentation output (https://tidyverse.tidyverse.org/). To double check, I also saved the file and looked at the .nbhtml version. I was able to get a condensed summary of conflicts with other packages


```{r}
# Running Help function to access information about a package
help(package="tidyverse")
```

Package: tidyverse
Title: Easily Install and Load the 'Tidyverse'
Version: 2.0.0
Authors@R: c(
    person("Hadley", "Wickham", , "hadley@rstudio.com", role = c("aut", "cre")),
    person("RStudio", role = c("cph", "fnd"))
  )
Description: The 'tidyverse' is a set of packages that work in harmony
    because they share common data representations and 'API' design. This
    package is designed to make it easy to install and load multiple
    'tidyverse' packages in a single step. Learn more about the
    'tidyverse' at <https://www.tidyverse.org>.
License: MIT + file LICENSE
URL: https://tidyverse.tidyverse.org,
        https://github.com/tidyverse/tidyverse
BugReports: https://github.com/tidyverse/tidyverse/issues
Depends: R (>= 3.3)
Imports: broom (>= 1.0.3), conflicted (>= 1.2.0), cli (>= 3.6.0),
        dbplyr (>= 2.3.0), dplyr (>= 1.1.0), dtplyr (>= 1.2.2), forcats
        (>= 1.0.0), ggplot2 (>= 3.4.1), googledrive (>= 2.0.0),
        googlesheets4 (>= 1.0.1), haven (>= 2.5.1), hms (>= 1.1.2),
        httr (>= 1.4.4), jsonlite (>= 1.8.4), lubridate (>= 1.9.2),
        magrittr (>= 2.0.3), modelr (>= 0.1.10), pillar (>= 1.8.1),
        purrr (>= 1.0.1), ragg (>= 1.2.5), readr (>= 2.1.4), readxl (>=
        1.4.2), reprex (>= 2.0.2), rlang (>= 1.0.6), rstudioapi (>=
        0.14), rvest (>= 1.0.3), stringr (>= 1.5.0), tibble (>= 3.1.8),
        tidyr (>= 1.3.0), xml2 (>= 1.3.3)
Suggests: covr (>= 3.6.1), feather (>= 0.3.5), glue (>= 1.6.2), mockr
        (>= 0.2.0), knitr (>= 1.41), rmarkdown (>= 2.20), testthat (>=
        3.1.6)
VignetteBuilder: knitr
Config/Needs/website: tidyverse/tidytemplate
Config/testthat/edition: 3
Encoding: UTF-8
RoxygenNote: 7.2.3
NeedsCompilation: no
Packaged: 2023-02-21 13:20:46 UTC; hadleywickham
Author: Hadley Wickham [aut, cre],
  RStudio [cph, fnd]
Maintainer: Hadley Wickham <hadley@rstudio.com>
Repository: CRAN
Date/Publication: 2023-02-22 09:20:06 UTC
Built: R 4.3.0; ; 2023-07-10 04:39:22 UTC; unix

# Assignment 2 


 
```{r}
MFIndD_analogy_read <- read_csv("/Users/jencuri/Documents/GitHub/Data2SciComm/WeeklyAssignments/tidy_data/MFIndD_analogy.csv")
```
1. The column qualtrics_id contains the unique identifier for each participant.




```{r}
?(MFIndD_analogy_read)
```

```{r}
glimpse(MFIndD_analogy_read)
```
2a. There are 792 rows in the dataset. There are 6 columns in the data set. I got this by using the ? function. Then I used the glimpse function to get the information. I verified by opening the csv file on excel to see the number of rows and numbers of columns. 


```{r}

MFIndD_analogy_read %>%
  distinct(qualtrics_id) %>%
  glimpse() 

```


```{r}

MFIndD_analogy_read %>%
   count(qualtrics_id) 
    
#Used to Verify
```


2b. There are 99 people in the dataset. 


```{r}
MFIndD_analogy_read %>%
  group_by(qualtrics_id) %>%
  summarise(num_of_trials = length(trial_number))
```
2c. Yes, everyone has data from the same number of trials. 





# Assignment 3 


```{r}
MFIndD_analogy_read %>%
  ungroup()
```

```{r}
summary_MFIndD_analogy <- MFIndD_analogy_read %>%
  group_by(qualtrics_id) %>%
  summarise(num_rel_matches = sum(response_type == "Rel"))
 
 
```


```{r}
(summary_MFIndD_analogy)
```



```{r}
summary_MFIndD_analogy %>%
  ggplot(aes(x = num_rel_matches)) +
  geom_histogram() +
  labs( x = "number of relational matches",
        y = "number of participants") +
  theme_minimal(
    
  )
```

2. There is a lot of variation in the number of relational matches chosen by participants, no uniformity. It looks like some participants consistently chose relational matches and others picking object matches more often.



```{r}
MFIndD_analogy_wider <- MFIndD_analogy_read %>%
  pivot_wider(id_cols = qualtrics_id,
              names_from = trial_number,
              values_from = response_type,
              names_sort = TRUE,
              names_prefix = "trial_")
  
```


```{r}
(MFIndD_analogy_wider)
```


```{r}


In the beginning, I was struggling with running my code chunk. I then realized that i had to ungroup any groupings I made in the previous assignment in order to start with the orignial data. 

I also tried to use count in this code chunk to try to show the numbers of trials for relational matches. But, it was not valid and I used sum instead. 
summary_MFIndD_analogy <- MFIndD_analogy_read %>%
  group_by(qualtrics_id) %>%
  summarise(num_rel_matches = count(response_type == "Rel"),
            eval=FALSE)

With the histogram, I tried to add a y column in the aes parameter but it came out as an error, I was then able to use labs to label my axis. 
summary_MFIndD_analogy %>%
  ggplot(aes(y = qualtrics_id
    x = num_rel_matches)) +
  geom_histogram() +
  labs( x = "number of relational matches",
        y = "number of participants") +
  theme_minimal(
    
  ),  eval=FALSE

```







# Assignment 4 

```{r}
MFIndD_REI_read <- read_csv("/Users/jencuri/Documents/GitHub/Data2SciComm/WeeklyAssignments/tidy_data/MFIndD_REI.csv")
```
```{r}
head(MFIndD_REI_read)
```
1. The column type of "response" is a character type and the column type for "scored_response" is a numeric (dbl). They are different because chr is assigned when a column contains mixed data types. For example, some values are numeric and some are strings. This classifies as chr. On the other hand, "scored_response" is classified as dbl bc the values are numeric values. 


```{r}
MFIndD_REI_read <- MFIndD_REI_read %>%
  mutate(response_double = case_when(
    response == "Strongly Disagree" ~ 1,
    response == "Strongly Agree" ~ 5,
    TRUE ~ as.double(response)
    
  )) 
```

```{r}
MFIndD_REI_read <- MFIndD_REI_read %>%
  mutate(new_scored_response = case_when(
    rev_scoring == "neg" ~ 6 - as.numeric(response_double),
    TRUE ~ as.numeric(response_double)
))
```

```{r}
head(MFIndD_REI_read)
```

```{r}
MFIndD_REI_read %>%
  filter(new_scored_response != scored_response)
```


# Assignment 5


```{r}
sum_MFIndD_REI_read <- MFIndD_REI_read %>%
  group_by(qualtrics_id, sub_type) %>% 
  summarize(score = sum(new_scored_response))

```
Null Values


```{r}
sum_MFIndD_REI_read <- MFIndD_REI_read %>%
  group_by(qualtrics_id, sub_type) %>% 
  summarize(score = sum(new_scored_response, na.rm = TRUE))

```
```{r}
head(sum_MFIndD_REI_read)
```


```{r}
is.na(sum_MFIndD_REI_read)

```

```{r}
combined_data <- full_join(sum_MFIndD_REI_read, summary_MFIndD_analogy, by = "qualtrics_id")
```



```{r}
ggplot(combined_data, aes(x = score, y = num_rel_matches, color = sub_type, lines = sub_type)) +
  geom_point(alpha = 0.7) + 
  geom_smooth(method = "lm", se = FALSE, color = "black") +  
  labs(
    title = "The Relation between REI Score and Analogy Score color coded by Subtype",
    x = "REI Score",
    y = "Analogy Score"
  ) +
  theme_minimal() +  
  theme(
    plot.title = element_text(hjust = 0.5)  # Center align the title
  )
```

Observations:
1. The subtypes are evenly distributed across both axes. No concentration of some sort. 
2. The trend lines meet seem to cross paths near the 40 mark.




# Assignment 6 

```{r}
MFIndD_probtask_read <-read.csv("/Users/jencuri/Documents/GitHub/Data2SciComm/WeeklyAssignments/tidy_data/MFIndD_probtask.csv")
```

```{r}
head(MFIndD_probtask_read)
```

```{r}
MFIndD_probtask_read %>%
  distinct(condition) %>%
  glimpse()
```
There are 4 distinct values in the "condition" column.

```{r}
distinct_condition_values <- c("dots_EqSizeSep","dots_EqSizeRand","blob_shifted","blob_stacked")
print(distinct_condition_values)
```

Pseudocode/Plan/Logic:
1. Vector with distinction condition values: Distinct_condition_values
2. Initialize an empty vector for mean reaction time. This is so that when the loop iterates, it stores the value in this vector. **Learned that I need to set it to the length of distinct_condition_values to avoid any other values 
3. Loop
  a. iterate over each index of distinct_condition_value 
  b. store the mean reaction time for the current condition at i. This makes sure that the mean is in the write place in the new vector. 
  c. select and filter the rows where the condition from the intial table matches with distinct_condition_value 
  d. now that the conditions matched, we can now look at corresponding rt
  e. Take the mean from the rt
  e. store in the vector mean_reaction_times

```{r}
mean_reaction_times <- numeric(length(distinct_condition_values))
```

```{r}
for (i in seq_along(distinct_condition_values)) {
  mean_reaction_times[i] <- mean(MFIndD_probtask_read$rt[MFIndD_probtask_read$condition == distinct_condition_values[i]])
}
print (mean_reaction_times)
```

When I ran this I got "[1] 889.8202 879.6184 892.2855 847.5153      NaN      NaN      NaN      NaN". When I first initialized mean_reaction_time, I had c() so I can store the values in here. But I realized I had to set it equal to the length of the vector of the distinct columns so there are no other values. I also added the numeric().

```{r}
accuracy_table_mean_across <- MFIndD_probtask_read %>%
  group_by(condition) %>%
  summarize(
    across(c(rt, correct), mean, na.rm = TRUE)
  )

print(accuracy_table_mean_across)
```


```{r}
accuracy_table_mean <- MFIndD_probtask_read %>%
  group_by(condition) %>%
  summarize(
    mean_rt = mean(rt, na.rm = TRUE),
    accuracy = mean(correct, na.rm = TRUE)
  )


print(accuracy_table_mean)
```


