---
title: "D2SC: Weekly Assignments"
author: "Jennifer Curi"
date: "`r Sys.Date()`"
output: html_notebook
---

# Initial Loading

```{r}
# loads tidyverse library
library(tidyverse)
```

# Week 1

I used Google to figure out how to load the tidyverse library. Specifically "How to add a 
code chunk that loads the tidy verse library".From there, I made sure to to use different credible websites to ensure that I find the correct code. The first website I opened was 
Stack Overflow (https://stackoverflow.com/questions/58289197/how-to-write-an-r-chunk-to-load-the-tidyverse).

However, I noticed that the comments were asking the user to clarify his question (i.e R Setup, or R Notebook, R Markdown). From this I employed another search clarifying that I am 
using R Notebook. From there I looked at another Stack Overflow forum (https://stackoverflow.com/questions/58568048/tidy-verse-issue) and I also looked at the 
 Tidyverse documentation (https://tidyverse.tidyverse.org/) on how to use the library. 
 
 To check that it was working, I ran the code and compared my Console output to the Tidyverse documentation output (https://tidyverse.tidyverse.org/). To double check, I also saved the file and looked at the .nbhtml version. I was able to get a condensed summary of conflicts with other packages


```{r}
# Running Help function to access information about a package
help(package="tidyverse")
```

Package: tidyverse
Title: Easily Install and Load the 'Tidyverse'
Version: 2.0.0
Authors@R: c(
    person("Hadley", "Wickham", , "hadley@rstudio.com", role = c("aut", "cre")),
    person("RStudio", role = c("cph", "fnd"))
  )
Description: The 'tidyverse' is a set of packages that work in harmony
    because they share common data representations and 'API' design. This
    package is designed to make it easy to install and load multiple
    'tidyverse' packages in a single step. Learn more about the
    'tidyverse' at <https://www.tidyverse.org>.
License: MIT + file LICENSE
URL: https://tidyverse.tidyverse.org,
        https://github.com/tidyverse/tidyverse
BugReports: https://github.com/tidyverse/tidyverse/issues
Depends: R (>= 3.3)
Imports: broom (>= 1.0.3), conflicted (>= 1.2.0), cli (>= 3.6.0),
        dbplyr (>= 2.3.0), dplyr (>= 1.1.0), dtplyr (>= 1.2.2), forcats
        (>= 1.0.0), ggplot2 (>= 3.4.1), googledrive (>= 2.0.0),
        googlesheets4 (>= 1.0.1), haven (>= 2.5.1), hms (>= 1.1.2),
        httr (>= 1.4.4), jsonlite (>= 1.8.4), lubridate (>= 1.9.2),
        magrittr (>= 2.0.3), modelr (>= 0.1.10), pillar (>= 1.8.1),
        purrr (>= 1.0.1), ragg (>= 1.2.5), readr (>= 2.1.4), readxl (>=
        1.4.2), reprex (>= 2.0.2), rlang (>= 1.0.6), rstudioapi (>=
        0.14), rvest (>= 1.0.3), stringr (>= 1.5.0), tibble (>= 3.1.8),
        tidyr (>= 1.3.0), xml2 (>= 1.3.3)
Suggests: covr (>= 3.6.1), feather (>= 0.3.5), glue (>= 1.6.2), mockr
        (>= 0.2.0), knitr (>= 1.41), rmarkdown (>= 2.20), testthat (>=
        3.1.6)
VignetteBuilder: knitr
Config/Needs/website: tidyverse/tidytemplate
Config/testthat/edition: 3
Encoding: UTF-8
RoxygenNote: 7.2.3
NeedsCompilation: no
Packaged: 2023-02-21 13:20:46 UTC; hadleywickham
Author: Hadley Wickham [aut, cre],
  RStudio [cph, fnd]
Maintainer: Hadley Wickham <hadley@rstudio.com>
Repository: CRAN
Date/Publication: 2023-02-22 09:20:06 UTC
Built: R 4.3.0; ; 2023-07-10 04:39:22 UTC; unix

# Assignment 2 


 
```{r}
MFIndD_analogy_read <- read_csv("/Users/jencuri/Documents/GitHub/Data2SciComm/WeeklyAssignments/tidy_data/MFIndD_analogy.csv")
```
1. The column qualtrics_id contains the unique identifier for each participant.




```{r}
?(MFIndD_analogy_read)
```

```{r}
glimpse(MFIndD_analogy_read)
```
2a. There are 792 rows in the dataset. There are 6 columns in the data set. I got this by using the ? function. Then I used the glimpse function to get the information. I verified by opening the csv file on excel to see the number of rows and numbers of columns. 


```{r}

MFIndD_analogy_read %>%
  distinct(qualtrics_id) %>%
  glimpse() 

```


```{r}

MFIndD_analogy_read %>%
   count(qualtrics_id) 
    
#Used to Verify
```


2b. There are 99 people in the dataset. 


```{r}
MFIndD_analogy_read %>%
  group_by(qualtrics_id) %>%
  summarise(num_of_trials = length(trial_number))
```
2c. Yes, everyone has data from the same number of trials. 





# Assignment 3 


```{r}
MFIndD_analogy_read %>%
  ungroup()
```

```{r}
summary_MFIndD_analogy <- MFIndD_analogy_read %>%
  group_by(qualtrics_id) %>%
  summarise(num_rel_matches = sum(response_type == "Rel"))
 
 
```


```{r}
(summary_MFIndD_analogy)
```



```{r}
summary_MFIndD_analogy %>%
  ggplot(aes(x = num_rel_matches)) +
  geom_histogram() +
  labs( x = "number of relational matches",
        y = "number of participants") +
  theme_minimal(
    
  )
```

2. There is a lot of variation in the number of relational matches chosen by participants, no uniformity. It looks like some participants consistently chose relational matches and others picking object matches more often.



```{r}
MFIndD_analogy_wider <- MFIndD_analogy_read %>%
  pivot_wider(id_cols = qualtrics_id,
              names_from = trial_number,
              values_from = response_type,
              names_sort = TRUE,
              names_prefix = "trial_")
  
```


```{r}
(MFIndD_analogy_wider)
```


```{r}


In the beginning, I was struggling with running my code chunk. I then realized that i had to ungroup any groupings I made in the previous assignment in order to start with the orignial data. 

I also tried to use count in this code chunk to try to show the numbers of trials for relational matches. But, it was not valid and I used sum instead. 
summary_MFIndD_analogy <- MFIndD_analogy_read %>%
  group_by(qualtrics_id) %>%
  summarise(num_rel_matches = count(response_type == "Rel"),
            eval=FALSE)

With the histogram, I tried to add a y column in the aes parameter but it came out as an error, I was then able to use labs to label my axis. 
summary_MFIndD_analogy %>%
  ggplot(aes(y = qualtrics_id
    x = num_rel_matches)) +
  geom_histogram() +
  labs( x = "number of relational matches",
        y = "number of participants") +
  theme_minimal(
    
  ),  eval=FALSE

```







# Assignment 4 

```{r}
MFIndD_REI_read <- read_csv("/Users/jencuri/Documents/GitHub/Data2SciComm/WeeklyAssignments/tidy_data/MFIndD_REI.csv")
```
```{r}
head(MFIndD_REI_read)
```
1. The column type of "response" is a character type and the column type for "scored_response" is a numeric (dbl). They are different because chr is assigned when a column contains mixed data types. For example, some values are numeric and some are strings. This classifies as chr. On the other hand, "scored_response" is classified as dbl bc the values are numeric values. 


```{r}
MFIndD_REI_read <- MFIndD_REI_read %>%
  mutate(response_double = case_when(
    response == "Strongly Disagree" ~ 1,
    response == "Disagree" ~ 2,
    response == "Neutral" ~ 3,
    response == "Agree" ~ 4,
    response == "Strongly Agree" ~ 5,
    TRUE ~ as.double(response)
    
  )) 
```

```{r}
MFIndD_REI_read <- MFIndD_REI_read %>%
  mutate(new_scored_response = case_when(
    rev_scoring == "neg" ~ 6 - as.numeric(scored_response),
    TRUE ~ as.numeric(scored_response)
))
```

```{r}
head(MFIndD_REI_read)
```

```{r}
MFIndD_REI_read %>%
  filter(new_scored_response != scored_response)
```

